BLAST: Block Applications for Things

### 2022-03-07 demo-eswc22/paper.tex
update

\begin{document}
%
\title{BLAST: Block Applications for Things}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Michael Freund\inst{1}\orcidID{0000-0003-1601-9331} \and
Thomas Wehr\inst{1}\orcidID{0000-0002-0678-5019} \and
Andreas Harth\inst{1,2}\orcidID{0000-0002-0702-510X}}
%
\authorrunning{M. Freund et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Fraunhofer Institute for Integrated Circuits IIS, Nürnberg, Germany 
\email{firstname.lastname@iis.fraunhofer.de}\\
\and
Friedrich–Alexander University Erlangen-Nürnberg, Nürnberg, Germany}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  An open research challenge in the deployment of IoT devices is the interaction with humans.
  We introduce a block-based visual programming language and execution environment called BLAST.
  BLAST allows for visually creating programs involving devices with a Web of Things interface.
  We demonstrate that BLAST can be used to create programs that interact with a variety of devices in different scenarios.
\keywords{Block-based Programming \and Web of Things.}
\end{abstract}
%
%
%
\setcounter{footnote}{0}
\section{Introduction}
IoT devices form the basis for a variety of applications, such as condition monitoring, energy consumption analysis, simulation and optimisation~\cite{CIMINO2019103130}.
However, there are still some research challenges that need to be overcome.
Interaction capabilities refer to the fact that devices will not be involved in any important decisions without humans.
In this paper, we focus on the challenge of humans interacting with devices, a challenge that needs to be resolved to achieve a widespread deployment of IoT devices in industry~\cite{KUEHNER20211227}.
Thus, humans should find it easy to interact with devices and the devices should be able to interact smoothly with humans.

@@

We present BLAST (Block Applications for Things), an easy-to-use interaction interface for humans with devices following the Web of Things interface based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}.
BLAST is a programming language with a focus on control flow constructs.

@@

\section{BLAST - Block Applications For Things}
Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}} library. %Momentan zweimal die gleiche Fußnote auf einer Seite.
Blockly is a pure JavaScript library for creating block-based languages and editors.
Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
We have named our block language ''Block Applications For Things'', or BLAST for short (See figure \ref{fig1}).
The browser-based BLAST uses web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD % Beides noch nicht definiert
 and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.

>>>>

\begin{document}
%
\title{BLAST: Block Applications for Things}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Michael Freund\inst{1}\orcidID{0000-0003-1601-9331} \and
Thomas Wehr\inst{1}\orcidID{0000-0002-0678-5019} \and
Andreas Harth\inst{1,2}\orcidID{0000-0002-0702-510X}}
%
\authorrunning{M. Freund et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Fraunhofer Institute for Integrated Circuits IIS, Nürnberg, Germany 
\email{firstname.lastname@iis.fraunhofer.de}\\
\and
Friedrich–Alexander University Erlangen-Nürnberg, Nürnberg, Germany}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  An open research challenge in the deployment of IoT devices is the interaction with humans.
  We introduce a block-based visual programming language and execution environment called BLAST.
  BLAST allows for visually creating programs involving devices with a Web of Things interface.
  We demonstrate that BLAST can be used to create programs that interact with a variety of devices in a geofencing scenario.
\keywords{Block-based Programming \and Web of Things.}
\end{abstract}
%
%
%
\setcounter{footnote}{0}
\section{Introduction}
IoT devices form the basis for a variety of applications, such as condition monitoring, energy consumption analysis, simulation and optimisation~\cite{CIMINO2019103130}.
However, there are still some research challenges that need to be overcome.
Interaction capabilities refer to the fact that devices will not be involved in any important decisions without humans.
In this paper, we focus on the challenge of humans interacting with devices, a challenge that needs to be resolved to achieve a widespread deployment of IoT devices in industry~\cite{KUEHNER20211227}.
Thus, humans should find it easy to interact with devices and the devices should be able to interact smoothly with humans.

@@

We present BLAST (Block Applications for Things), an easy-to-use interaction interface for humans with devices following the Web of Things interface based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}.
BLAST is a programming language with a focus on control flow constructs.
BLAST implements the Web of Things abstraction to devices with Bluetooth Low Energy (BLE) and USB Human Interface Devices (HID) interface and to various browser APIs that allow for accessing HTTP APIs.
These devices and APIs are supported by modern web browsers.

@@

\section{BLAST - Block Applications For Things}

Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}} library. %Momentan zweimal die gleiche Fußnote auf einer Seite.
Blockly is a pure JavaScript library for creating block-based languages and editors.
Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
We have named our block language ''Block Applications For Things'', or BLAST for short (See figure \ref{fig1}).
The browser-based BLAST uses web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD % Beides noch nicht definiert
 and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.
